---
title: "Kaggle survey visulization inspired from Bukun"
author: "Yuqing Xue"
date: "November 2, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(DT) # datatable
library(stringr)
# library for 'UQ'
```

```{r message = FALSE, warning = FALSE}
freeformResponses = read_csv("/Users/apple/Desktop/Yuqing R Work/Kaggle!/kaggle-survey-2017/freeformResponses.csv")

multipleChoiceResponses = read_csv("/Users/apple/Desktop/Yuqing R Work/Kaggle!/kaggle-survey-2017/multipleChoiceResponses.csv")

schema = read_csv("/Users/apple/Desktop/Yuqing R Work/Kaggle!/kaggle-survey-2017/schema.csv")
```

```{r}
# colnames(multipleChoiceResponses)
nrow(multipleChoiceResponses)

```

```{r}
# table(multipleChoiceResponses$Country)
```

<br>



#### Data Cleaning: China /Taiwan (overwrite the dataset)
```{r}
multipleChoiceResponses = multipleChoiceResponses %>%
  mutate(Country = ifelse(Country == "Republic of China", "Taiwan", 
                            ifelse(Country == "People 's Republic of China", "China",
                                   Country)))
```

##### To ensure that we keep our raw data un-touched, we'll create a duplicate dataframe called "cleanMCR"

```{r}
cleanMCR <- multipleChoiceResponses
```
#### cool colors 

<http://www.colorhexa.com/b2ba0b>
```{r}
coolLightBlue = "#54c6f5"
# coolYellow = "#F1C40F" 
coolLightGreen = "#7aaa0a"
```

<br>

####  A. Which country has the youngest data scientists? 
##### 1. Data Preparation

```{r}
cleanMCR %>%
  filter(!is.na(Country)) %>%  
  group_by(Country) %>%
  summarise(AgeMedian = median(Age,na.rm = TRUE)) %>%
  # ungroup() %>%
  mutate(Country = reorder(Country,AgeMedian)) %>%  # order Country by AgeMedian
  arrange(AgeMedian) %>%  # default is ascending
  head(15) 
```

```{r Nov.6 Mon add AgeMean,datatable}
cleanMCR %>%
  filter(!is.na(Country)) %>%  
  group_by(Country) %>%
  summarise(AgeMedian = median(Age,na.rm = TRUE), AgeMean = round(mean(Age, na.rm = TRUE), digit = 1)) %>%
  # ungroup() %>%
  # mutate(Country = reorder(Country,AgeMedian)) %>%  # order Country by AgeMedian
  arrange(AgeMedian) %>%  # default is ascending. !not arrange(AgeMedian, AgeMean)
  datatable(filter = 'top', 
            #options = list(pageLength = 15),
             caption = htmltools::tags$caption(
               style = 'caption-side: bottom; text-align: center;',
                'Table 1. ', htmltools::em('Median and Mean Ages of Respondents by Country.')
    )
  )
  
```


```{r checkAgeResult}
cleanMCR %>% 
  filter(Country == 'China') %>%
  summarise(meanAge = mean(Age, na.rm = T), medianAge = median(Age, na.rm = T))
```


<br>

`datatable`: Inspired from <https://www.kaggle.com/ikleiman/data-scientists-salaries-around-the-world> 

Documentation from <https://rstudio.github.io/DT/>

<br>

##### 2. Barplot Initiating


```{r}
cleanMCR %>%
  filter(!is.na(Country)) %>%
  group_by(Country) %>%
  summarise(AgeMedian = median(Age,na.rm = TRUE)) %>%
  # ungroup() %>%
  mutate(Country = reorder(Country,AgeMedian)) %>%
  arrange(AgeMedian) %>%
  head(10) %>%  # 
  
  ggplot(aes(x = Country,y = AgeMedian)) +
  geom_bar(stat = 'identity', fill = coolLightGreen) 
```

`stat = 'identity'`: The heights of the bars commonly represent one of two things: either a count of cases in each group, or the values in a column of the data frame. By default, geom_bar uses stat="bin". This makes the height of each bar equal to the number of cases in each group, and it is incompatible with mapping values to the y aesthetic. If you want the heights of the bars to represent values in the data, use stat="identity" and map a value to the y aesthetic.

[geom_bar, stat = 'identity'](https://www.rdocumentation.org/packages/ggplot2/versions/1.0.1/topics/geom_bar)



<br>

##### 3. Adjusting and Polishing 

```{r}
nsample = 10

cleanMCR %>%
  filter(!is.na(Country)) %>%
  group_by(Country) %>%
  summarise(AgeMedian = median(Age,na.rm = TRUE)) %>%
  # ungroup() %>%
  mutate(Country = reorder(Country,AgeMedian)) %>%
  arrange(AgeMedian) %>%
  head(nsample) %>%  # elegant way
  
  ggplot(aes(x = Country,y = AgeMedian, label = AgeMedian)) +
  geom_bar(stat = 'identity', fill = coolLightGreen) +
  geom_label(hjust = 0.5, vjust = 0.5, size = 3.3) + 
  labs(x = "", y = "Median age of the responders", title = str_c("Top ", nsample, " ", "Country With the Youngest Data Scientist Talent" )) + 
  coord_flip() + 
  # theme_bw()   # dark-on-light, work better for presentations
  theme_gray()
```


<br>

####  B. Gender Distribution
##### 1. Data Preparation

```{r}
NoOfRows = nrow(cleanMCR)
createLabel = function(Count,NoOfRows)
{
  return ( str_c(" ( ", Count, " - ", round(Count/NoOfRows,digit = 2), " %)"  ) )
}

cleanMCR %>%
  filter(!is.na(GenderSelect)) %>%  
  group_by(GenderSelect) %>%
  summarise(count = n()) %>%  # like table in base R to deal with categorical data
  ungroup() %>%
  mutate(GenderSelect = reorder(GenderSelect, count)) %>%  # order Country by AgeMedian
  arrange(desc(count)) # default is ascending
```

##### A better approach to generate these tables is through function, which can be learned from a kernel from `Amber Thomas`, whose multiple kernels were used in the official Kaggle report. [Amber Thomas's kernel](https://www.kaggle.com/amberthomas/kaggle-2017-survey-results)

```{r}
# A function to analyze questions where you choose only one answer
chooseOne = function(question, filteredData = cleanMCR){
  
  filteredData %>% 
    # Remove any rows where the respondent didn't answer the question
    filter(!UQ(sym(question)) == "") %>% 
    # Group by the responses to the question
    group_by_(question) %>% 
    # Count how many respondents selected each option
    summarise(count = n()) %>% 
    # Calculate what percent of respondents selected each option
    mutate(percent = (count / sum(count)) * 100) %>% 
    # Arrange the counts in descending order
    arrange(desc(count))
}
  
```

```{r}
chooseOne("GenderSelect")
```



#### A Table like this should be suffice. If a barplot is desired, then it can be created in this way:

```{r}
NoOfRows = nrow(multipleChoiceResponses)
# create a function to put percentage on bars
labelPerc = function(Count,NoOfRows)
{
  return( str_c("( ", Count, " - ", round(Count/NoOfRows * 100, digit = 2), "%)"  ) )
}


multipleChoiceResponses %>%
  filter(!is.na(GenderSelect)) %>%  
  group_by(GenderSelect) %>%
  summarise(count = n()) %>%  # like table in base R to deal with categorical data
  ungroup() %>%
  mutate(GenderSelect = reorder(GenderSelect, count)) %>%  # order Country by AgeMedian
  arrange(desc(count)) %>%  # default is ascending
  
  ggplot(aes(x = GenderSelect,y = count)) +
  geom_bar(stat = 'identity', fill = coolLightBlue) +
  geom_text(aes(x = GenderSelect, y = 0, label = labelPerc(count,NoOfRows) ),
            hjust = 0, vjust = .5, size = 4, colour = 'black', family = "sans",
            fontface = 'bold') +  # bold, plain
  labs(x = '', 
       y = 'Gender Frequency Count', 
       title = 'Gender Frequency and Percentage Among All ') +
  coord_flip() 
```





